---
title: "Panel Count vs Size by Page"
author: "Drew Hendrickson"
date: "`r Sys.Date()`"
output: html_document
---

# Measure the effect of predictors on Page Count (per Page)

### First, read, clean, and select the data

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries}

library(tidyverse)
library(lme4)
library(pander)

```




```{r read_and_format_data}



source("paths.R")

data <- read_csv(paste0(clean_path, "page_data.csv"))

data$DocumentID <- factor(data$Document.Directory)
data$RegionSimplified <- factor(data$RegionSimplified)
data$StyleBroad <- factor(data$StyleBroad)
data$Page <- factor(data$Page.Number)
data$Year <- factor(data$Publication.Date)

```

```{r select_vars}

data <- data %>%
  select(panel_count, panel_size_prop_mean,
         Year, RegionSimplified, StyleBroad,
         LangFinal_WordStructureRaw,
         LangFinal_WALS_VerbInflection,
         DocumentID, Page)

str(data)

```

# Data Inspection

```{r panel_count_by_size_plot}

ggplot(data,
       aes(x = panel_size_prop_mean,
           y = panel_count)) +
  geom_point(alpha=0.5) +
  theme_bw()



```

## log transform measures and drop original

```{r add_log_transformations}


data$log_panel_size <- log(data$panel_size_prop_mean, 10)
data$log_panel_count <- log(data$panel_count, 10)

data <- data %>%
  select(-panel_size_prop_mean, -panel_count)

str(data)
```

## relationship between log(panel size) and log(panel count)

```{r log_plot}

ggplot(data,
       aes(x = log_panel_size,
           y = log_panel_count)) +
  geom_point(alpha=0.5) +
  theme_bw()

```



# Checking effect of interaction between panel size and various variables

## Effect of interaction between log(panel_size) and style

What is the effect of the interaction between log(panel_size) and style when added to a model with all other factors AND interactions:

- Style and Word Structure 
- Style and Verb Inflection 
- Region and Word Structure 
- Region and Verb Inflection 
- Word Structure and Verb Inflection
- Region and log(panel size)
- Word Structure and log(panel size)
- Verb Inflection and log(panel size)

```{r style_size_interaction_effect}



full_model <- lmer(log_panel_count ~ log_panel_size +
                     StyleBroad +
                     StyleBroad : log_panel_size +
                     RegionSimplified +
                     RegionSimplified : log_panel_size +
                     # StyleBroad : RegionSimplified +
                     LangFinal_WordStructureRaw +
                     log_panel_size : LangFinal_WordStructureRaw +
                     StyleBroad : LangFinal_WordStructureRaw +
                     RegionSimplified : LangFinal_WordStructureRaw +
                     LangFinal_WALS_VerbInflection +
                     log_panel_size : LangFinal_WALS_VerbInflection +
                     StyleBroad : LangFinal_WALS_VerbInflection +
                     RegionSimplified : LangFinal_WALS_VerbInflection +
                     LangFinal_WordStructureRaw : LangFinal_WALS_VerbInflection +
                     Year +
                     (1 | DocumentID),
                   data = data)



alt_model <- lmer(log_panel_count ~ log_panel_size +
                     StyleBroad +
                     #StyleBroad : log_panel_size +
                     RegionSimplified +
                     RegionSimplified : log_panel_size +
                     # StyleBroad : RegionSimplified +
                     LangFinal_WordStructureRaw +
                     log_panel_size : LangFinal_WordStructureRaw +
                     StyleBroad : LangFinal_WordStructureRaw +
                     RegionSimplified : LangFinal_WordStructureRaw +
                     LangFinal_WALS_VerbInflection +
                     log_panel_size : LangFinal_WALS_VerbInflection +
                     StyleBroad : LangFinal_WALS_VerbInflection +
                     RegionSimplified : LangFinal_WALS_VerbInflection +
                     LangFinal_WordStructureRaw : LangFinal_WALS_VerbInflection +
                     Year +
                     (1 | DocumentID),
                   data = data)

pander( anova(alt_model, full_model) )

```



## Effect of interaction between log(panel_size) and region

What is the effect of the interaction between log(panel_size) and region when added to a model with all other factors AND interactions:

- Style and Word Structure 
- Style and Verb Inflection 
- Style and log(panel size)
- Region and Word Structure 
- Region and Verb Inflection 
- Word Structure and Verb Inflection
- Word Structure and log(panel size)
- Verb Inflection and log(panel size)

```{r region_size_interaction_effect}



full_model <- lmer(log_panel_count ~ log_panel_size +
                     StyleBroad +
                     StyleBroad : log_panel_size +
                     RegionSimplified +
                     RegionSimplified : log_panel_size +
                     # StyleBroad : RegionSimplified +
                     LangFinal_WordStructureRaw +
                     log_panel_size : LangFinal_WordStructureRaw +
                     StyleBroad : LangFinal_WordStructureRaw +
                     RegionSimplified : LangFinal_WordStructureRaw +
                     LangFinal_WALS_VerbInflection +
                     log_panel_size : LangFinal_WALS_VerbInflection +
                     StyleBroad : LangFinal_WALS_VerbInflection +
                     RegionSimplified : LangFinal_WALS_VerbInflection +
                     LangFinal_WordStructureRaw : LangFinal_WALS_VerbInflection +
                     Year +
                     (1 | DocumentID),
                   data = data)



alt_model <- lmer(log_panel_count ~ log_panel_size +
                     StyleBroad +
                     StyleBroad : log_panel_size +
                     RegionSimplified +
                     #RegionSimplified : log_panel_size +
                     # StyleBroad : RegionSimplified +
                     LangFinal_WordStructureRaw +
                     log_panel_size : LangFinal_WordStructureRaw +
                     StyleBroad : LangFinal_WordStructureRaw +
                     RegionSimplified : LangFinal_WordStructureRaw +
                     LangFinal_WALS_VerbInflection +
                     log_panel_size : LangFinal_WALS_VerbInflection +
                     StyleBroad : LangFinal_WALS_VerbInflection +
                     RegionSimplified : LangFinal_WALS_VerbInflection +
                     LangFinal_WordStructureRaw : LangFinal_WALS_VerbInflection +
                     Year +
                     (1 | DocumentID),
                   data = data)

pander( anova(alt_model, full_model) )

```




## Effect of interaction between log(panel_size) and Word Structure

What is the effect of the interaction between log(panel_size) and Word Structure when added to a model with all other factors AND interactions:

- Style and Word Structure 
- Style and Verb Inflection 
- Style and log(panel size)
- Region and Word Structure 
- Region and Verb Inflection 
- Region and log(panel size)
- Word Structure and Verb Inflection
- Verb Inflection and log(panel size)

```{r structure_size_interaction_effect}



full_model <- lmer(log_panel_count ~ log_panel_size +
                     StyleBroad +
                     StyleBroad : log_panel_size +
                     RegionSimplified +
                     RegionSimplified : log_panel_size +
                     # StyleBroad : RegionSimplified +
                     LangFinal_WordStructureRaw +
                     log_panel_size : LangFinal_WordStructureRaw +
                     StyleBroad : LangFinal_WordStructureRaw +
                     RegionSimplified : LangFinal_WordStructureRaw +
                     LangFinal_WALS_VerbInflection +
                     log_panel_size : LangFinal_WALS_VerbInflection +
                     StyleBroad : LangFinal_WALS_VerbInflection +
                     RegionSimplified : LangFinal_WALS_VerbInflection +
                     LangFinal_WordStructureRaw : LangFinal_WALS_VerbInflection +
                     Year +
                     (1 | DocumentID),
                   data = data)



alt_model <- lmer(log_panel_count ~ log_panel_size +
                     StyleBroad +
                     StyleBroad : log_panel_size +
                     RegionSimplified +
                     RegionSimplified : log_panel_size +
                     # StyleBroad : RegionSimplified +
                     LangFinal_WordStructureRaw +
                     #log_panel_size : LangFinal_WordStructureRaw +
                     StyleBroad : LangFinal_WordStructureRaw +
                     RegionSimplified : LangFinal_WordStructureRaw +
                     LangFinal_WALS_VerbInflection +
                     log_panel_size : LangFinal_WALS_VerbInflection +
                     StyleBroad : LangFinal_WALS_VerbInflection +
                     RegionSimplified : LangFinal_WALS_VerbInflection +
                     LangFinal_WordStructureRaw : LangFinal_WALS_VerbInflection +
                     Year +
                     (1 | DocumentID),
                   data = data)

pander( anova(alt_model, full_model) )

```


## Effect of interaction between log(panel_size) and Verb Inflection

What is the effect of the interaction between log(panel_size) and Verb Inflection when added to a model with all other factors AND interactions:

- Style and Word Structure 
- Style and Verb Inflection 
- Style and log(panel size)
- Region and Word Structure 
- Region and Verb Inflection 
- Region and log(panel size)
- Word Structure and Verb Inflection
- Word Structure and log(panel size)

```{r inflection_size_interaction_effect}



full_model <- lmer(log_panel_count ~ log_panel_size +
                     StyleBroad +
                     StyleBroad : log_panel_size +
                     RegionSimplified +
                     RegionSimplified : log_panel_size +
                     # StyleBroad : RegionSimplified +
                     LangFinal_WordStructureRaw +
                     log_panel_size : LangFinal_WordStructureRaw +
                     StyleBroad : LangFinal_WordStructureRaw +
                     RegionSimplified : LangFinal_WordStructureRaw +
                     LangFinal_WALS_VerbInflection +
                     log_panel_size : LangFinal_WALS_VerbInflection +
                     StyleBroad : LangFinal_WALS_VerbInflection +
                     RegionSimplified : LangFinal_WALS_VerbInflection +
                     LangFinal_WordStructureRaw : LangFinal_WALS_VerbInflection +
                     Year +
                     (1 | DocumentID),
                   data = data)



alt_model <- lmer(log_panel_count ~ log_panel_size +
                     StyleBroad +
                     StyleBroad : log_panel_size +
                     RegionSimplified +
                     RegionSimplified : log_panel_size +
                     # StyleBroad : RegionSimplified +
                     LangFinal_WordStructureRaw +
                     log_panel_size : LangFinal_WordStructureRaw +
                     StyleBroad : LangFinal_WordStructureRaw +
                     RegionSimplified : LangFinal_WordStructureRaw +
                     LangFinal_WALS_VerbInflection +
                     #log_panel_size : LangFinal_WALS_VerbInflection +
                     StyleBroad : LangFinal_WALS_VerbInflection +
                     RegionSimplified : LangFinal_WALS_VerbInflection +
                     LangFinal_WordStructureRaw : LangFinal_WALS_VerbInflection +
                     Year +
                     (1 | DocumentID),
                   data = data)

pander( anova(alt_model, full_model) )

```

