---
title: "Panel Count by Page"
author: "Drew Hendrickson"
date: "`r Sys.Date()`"
output: html_document
---

# Measure the effect of predictors on Page Count (per Page)

### First, read, clean, and select the data

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries}

library(tidyverse)
library(lme4)
library(pander)

```




```{r read_and_format_data}



source("paths.R")

data <- read_csv(paste0(clean_path, "page_data.csv"))

data$DocumentID <- factor(data$Document.Directory)
data$RegionSimplified <- factor(data$RegionSimplified)
data$StyleBroad <- factor(data$StyleBroad)
data$Page <- factor(data$Page.Number)
data$Year <- factor(data$Publication.Date)

```

```{r select_vars}

data <- data %>%
  select(panel_count, 
         Year, RegionSimplified, StyleBroad,
         LangFinal_WordStructureRaw,
         LangFinal_WALS_VerbInflection,
         DocumentID, Page)

str(data)

```

# Inspect the data


### Region by Style

Unfortunately some Styles are only in a few Regions, this makes the interaction hard to model.

```{r }

pander( table(data$RegionSimplified, data$StyleBroad) )

```




# Now, we look at model comparisons

## Effect of style

What is the effect of style when added to a model with all other factors

```{r style_analysis}

full_model <- lmer(panel_count ~ StyleBroad + RegionSimplified + 
                     Year + LangFinal_WordStructureRaw + 
                     LangFinal_WALS_VerbInflection + (1 | DocumentID),
                   data = data)

alt_model <- lmer(panel_count ~ RegionSimplified + 
                    Year + LangFinal_WordStructureRaw + 
                    LangFinal_WALS_VerbInflection + (1 | DocumentID),
                  data = data)

pander( anova(alt_model, full_model) )

```

What is the effect of style when added to a model with all other factors AND 5 interactions:

- Style and Word Structure 
- Style and Verb Inflection 
- Region and Word Structure 
- Region and Verb Inflection 
- Word Structure and Verb Inflection


```{r style_analysis_with_interactions}

full_model <- lmer(panel_count ~ StyleBroad + RegionSimplified + 
                     # StyleBroad : RegionSimplified + 
                     LangFinal_WordStructureRaw + 
                     StyleBroad : LangFinal_WordStructureRaw +
                     RegionSimplified : LangFinal_WordStructureRaw +
                     LangFinal_WALS_VerbInflection + 
                     StyleBroad : LangFinal_WALS_VerbInflection +
                     RegionSimplified : LangFinal_WALS_VerbInflection +
                     LangFinal_WordStructureRaw : LangFinal_WALS_VerbInflection +
                     Year + 
                     (1 | DocumentID),
                   data = data)

alt_model <- lmer(panel_count ~ RegionSimplified + 
                    # StyleBroad : RegionSimplified + 
                    LangFinal_WordStructureRaw + 
                    StyleBroad : LangFinal_WordStructureRaw +
                    RegionSimplified : LangFinal_WordStructureRaw +
                    LangFinal_WALS_VerbInflection + 
                    StyleBroad : LangFinal_WALS_VerbInflection +
                    RegionSimplified : LangFinal_WALS_VerbInflection +
                    LangFinal_WordStructureRaw : LangFinal_WALS_VerbInflection +
                    Year + 
                   (1 | DocumentID),
                  data = data)


pander( anova(alt_model, full_model) )

```

## Effect of Region

What is the effect of region when added to a model with all other factors

```{r region_analysis}

full_model <- lmer(panel_count ~ StyleBroad + RegionSimplified + 
                     Year + LangFinal_WordStructureRaw + 
                     LangFinal_WALS_VerbInflection + (1 | DocumentID),
                   data = data)

alt_model <- lmer(panel_count ~ StyleBroad + 
                    Year + LangFinal_WordStructureRaw + 
                    LangFinal_WALS_VerbInflection + (1 | DocumentID),
                  data = data)

pander( anova(alt_model, full_model) )

```



## Effect of Word Structure

What is the effect of Word Structure when added to a model with all other factors

```{r Word_Structure_analysis}

full_data <- data[!is.na(data$LangFinal_WordStructureRaw),]

full_model <- lmer(panel_count ~ StyleBroad + RegionSimplified + 
                     Year + LangFinal_WordStructureRaw + 
                     LangFinal_WALS_VerbInflection + (1 | DocumentID),
                   data = full_data)

alt_model <- lmer(panel_count ~ StyleBroad + RegionSimplified +
                    Year + 
                    LangFinal_WALS_VerbInflection + (1 | DocumentID),
                  data = full_data)

pander( anova(alt_model, full_model) )

```


## Effect of Verb Inflection

What is the effect of WALS Verb Inflection when added to a model with all other factors

```{r WALS_VerbInflection_analysis}

full_data <- data[!is.na(data$LangFinal_WALS_VerbInflection),]

full_model <- lmer(panel_count ~ StyleBroad + RegionSimplified + 
                     Year + LangFinal_WordStructureRaw + 
                     LangFinal_WALS_VerbInflection + (1 | DocumentID),
                   data = full_data)

alt_model <- lmer(panel_count ~ StyleBroad + RegionSimplified +
                    Year + LangFinal_WordStructureRaw
                  + (1 | DocumentID),
                  data = full_data)

pander( anova(alt_model, full_model) )

```


## Effect of Year

What is the effect of Year when added to a model with all other factors

```{r year_analysis}

full_model <- lmer(panel_count ~ StyleBroad + RegionSimplified + 
                     Year + LangFinal_WordStructureRaw + 
                     LangFinal_WALS_VerbInflection + (1 | DocumentID),
                   data = data)

alt_model <- lmer(panel_count ~ StyleBroad + RegionSimplified +
                    LangFinal_WordStructureRaw +
                    LangFinal_WALS_VerbInflection + (1 | DocumentID),
                  data = data)

pander( anova(alt_model, full_model) )

```
