---
title: "Main effects of Region and Style on Average Panel Size per Page"
author: "Drew Hendrickson"
date: "`r Sys.Date()`"
output: html_document
---

### First, read, clean, and select the data

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries}

library(tidyverse)
library(lme4)
library(pander)
library(ggplot2)
library(emmeans)


```




```{r read_and_format_data}



source("paths.R")

data <- read_csv(paste0(clean_path, "page_data.csv"))

data$DocumentID <- factor(data$Document.Directory)
data$RegionSimplified <- factor(data$RegionSimplified)
data$StyleBroad <- factor(data$StyleBroad)
data$Page <- factor(data$Page.Number)
data$Year <- factor(data$Publication.Date)

```

```{r select_vars}

data <- data %>%
  select(panel_size_prop_mean, 
         Year, RegionSimplified, StyleBroad,
         LangFinal_WordStructureRaw,
         LangFinal_WALS_VerbInflection,
         DocumentID, Page)

str(data)

```

# Now, we look at model comparisons


## Effect of Region

Is there a main effect of region compared to the full model without interactions?

```{r region_analysis}

full_model <- lmer(panel_size_prop_mean ~ StyleBroad + RegionSimplified + 
                     Year + LangFinal_WordStructureRaw + 
                     LangFinal_WALS_VerbInflection + (1 | DocumentID),
                   data = data)

alt_model <- lmer(panel_size_prop_mean ~ StyleBroad + 
                    Year + LangFinal_WordStructureRaw + 
                    LangFinal_WALS_VerbInflection + (1 | DocumentID),
                  data = data)

pander( anova(alt_model, full_model) )

```


```{r post-hoc-region-analysis}

#emmeans(full_model, "RegionSimplified", pbkrtest.limit = 14000)


results <- emmeans(full_model,
        list(pairwise ~ RegionSimplified),
        adjust = "tukey",
        pbkrtest.limit = 14000)

results <- as.data.frame(results$`pairwise differences of RegionSimplified`)

results[results$p.value < 0.1,]

```

## Plot of the effect of Region


```{r plot-region}

ggplot(data,
       aes(x = RegionSimplified, 
           y = panel_size_prop_mean)) +
  geom_boxplot() +
  theme_bw() +
  labs(x = "Region",
       y = "Panels per Page",
       fill = "Style") +
  theme(legend.position="top",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
  

```

## Effect of Style

Is there a main effect of style compared to the full model without interactions?

```{r style_analysis}

full_model <- lmer(panel_size_prop_mean ~ StyleBroad + RegionSimplified + 
                     Year + LangFinal_WordStructureRaw + 
                     LangFinal_WALS_VerbInflection + (1 | DocumentID),
                   data = data)

alt_model <- lmer(panel_size_prop_mean ~ RegionSimplified + 
                    Year + LangFinal_WordStructureRaw + 
                    LangFinal_WALS_VerbInflection + (1 | DocumentID),
                  data = data)

pander( anova(alt_model, full_model) )

```

```{r post-hoc-style-analysis}

results <- emmeans(full_model,
        list(pairwise ~ StyleBroad),
        adjust = "tukey",
        pbkrtest.limit = 14000)

results <- as.data.frame(results$`pairwise differences of StyleBroad`)

results[results$p.value < 0.1,]

```

## Plot of the effect of Style


```{r plot-style}

ggplot(data,
       aes(x = StyleBroad, 
           y = panel_size_prop_mean)) +
  geom_boxplot() +
  theme_bw() +
  labs(x = "Style",
       y = "Panels per Page",
       fill = "Style") +
  theme(legend.position="top",
        axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
  

```



############


## Effect of Word Structure

Is there a main effect of word structure compared to the full model without interactions?

```{r word_structure_analysis}

full_data <- data[!is.na(data$LangFinal_WordStructureRaw),]

print(paste0("Dropped ", sum(is.na(data$LangFinal_WordStructureRaw)),
      " rows from the full dataset with ", nrow(data)))

full_model <- lmer(panel_size_prop_mean ~ StyleBroad + RegionSimplified + 
                     Year + LangFinal_WordStructureRaw + 
                     LangFinal_WALS_VerbInflection + (1 | DocumentID),
                   data = full_data)

alt_model <- lmer(panel_size_prop_mean ~ StyleBroad + RegionSimplified + 
                    Year +  
                    LangFinal_WALS_VerbInflection + (1 | DocumentID),
                  data = full_data)

pander( anova(alt_model, full_model) )

```


## Plot of the effect of Word Structure


```{r plot-word-structure}

ggplot(data,
       aes(x = LangFinal_WordStructureRaw, 
           y = panel_size_prop_mean)) +
  geom_point(alpha = 0.3) +
  geom_smooth(method='lm') + 
  theme_bw() +
  labs(x = "Word Structure Score",
       y = "Panels per Page",
       fill = "Style") +
  theme(legend.position="top")
  

```


############


## Effect of Verb Inflection

Is there a main effect of verb inflection compared to the full model without interactions?

```{r verb_inflection_analysis}

full_data <- data[!is.na(data$LangFinal_WALS_VerbInflection),]

print(paste0("Dropped ", sum(is.na(data$LangFinal_WALS_VerbInflection)),
      " rows from the full dataset with ", nrow(data)))

full_model <- lmer(panel_size_prop_mean ~ StyleBroad + RegionSimplified + 
                     Year + LangFinal_WordStructureRaw + 
                     LangFinal_WALS_VerbInflection + (1 | DocumentID),
                   data = full_data)

alt_model <- lmer(panel_size_prop_mean ~ StyleBroad + RegionSimplified + 
                    Year + LangFinal_WordStructureRaw + (1 | DocumentID),
                  data = full_data)

pander( anova(alt_model, full_model) )

```


## Plot of the effect of Verb Inflection


```{r plot-verb-inflection}

ggplot(data,
       aes(x = LangFinal_WALS_VerbInflection, 
           y = panel_size_prop_mean)) +
  geom_point(alpha = 0.1) +
  geom_smooth(method='lm') + 
  theme_bw() +
  labs(x = "Verb Inflection Score",
       y = "Panels per Page",
       fill = "Style") +
  theme(legend.position="top")
  

```

